Standalone Tactics using OpenTheory

### 2012-01-17 paper.tex
some references

For instance, Kumar and Weber~\cite{DBLP:conf/itp/KumarW11} and Kun\v{c}ar~\cite{DBLP:conf/itp/Kuncar11} give independent integrations of a quantified boolean formula solver into a higher-order logic based system (HOL4 in one case and HOL Light in the other).
Weber and Amjad~\cite{weber09efficiently} give high-performance integrations of SAT solvers into three HOL-based systems (HOL4, HOL Light, and Isabelle/HOL); each integration requires a separate implementation.
<Metis integrated many times separately; currenty HOL4 version is very old and upgrading would be painful>
<Sledgehammer <ref> regarded as one of the most successful integrations <ref> is available for Isabelle only, but the ideas behind it don't intrinsically exclude HOL4, HOL Light, etc.>
<TFL, function package,>
Certain kinds of functionality, or improvements in functionality (e.g. Isabelle function package over TFL) become restricted to a single proof assistant unnecessarily.
<datatype packages>
<arithmetic decision procedures>

@@

Evidential tool bus.
System on TPTP.
Omega.
Natural extension of the integration of automatic tools into interactive systems.

>>>>

For instance, Kumar and Weber~\cite{DBLP:conf/itp/KumarW11} and Kun\v{c}ar~\cite{DBLP:conf/itp/Kuncar11} give independent integrations of a quantified boolean formula solver into a higher-order logic based system (HOL4 in one case and HOL Light in the other).
Weber and Amjad~\cite{weber09efficiently} give high-performance integrations of SAT solvers into three HOL-based systems (HOL4, HOL Light, and Isabelle/HOL); each integration requires a separate implementation.
<Metis integrated many times separately; currenty HOL4 version is very old and upgrading would be painful>
<Sledgehammer~\cite{DBLP:journals/japll/MengP09,Paulson_threeyears} is available for Isabelle only, but the ideas behind it don't intrinsically exclude HOL4, HOL Light, etc.>
<TFL, function package,>
Certain kinds of functionality, or improvements in functionality (e.g. Isabelle function package over TFL) become restricted to a single proof assistant unnecessarily.
<datatype packages>
<arithmetic decision procedures>

@@

System on TPTP~\cite{DBLP:conf/lpar/Sutcliffe10}.
<Comparison to THF?>
Evidential tool bus~\cite{DBLP:conf/icfem/Rushby05,fk:etb}.
Omega.
Natural extension of the integration of automatic tools into interactive systems.
